---
title: "1. Basic Information"
format: html
---

```{r}
library(readr)
library(downloadthis)
library(DT)
library(dplyr)
library(here)
library(httr2)
library(jsonlite)
source(here::here('functions/load_functions.R'))
load_functions()
```

## Basic Information

### Community Hospitals of Central California (CHCC)

**EIN: 942437106**

When Googling CHCC @community_medical_centers, the website that comes up first is "Community Medical Centers" @community_medical_centers and not "Community Hospitals of Central California".

CHCC has a sort of confusing website setup. First, they have a website called communitymedical.org @community_medical_centers. This site appears to be dedicated
to the 4 Fresno and Clovis medical centers (listed below). However, they have a second website called cmcenters.org @cmcenters, which has a much longer list of medical centers and administrative buildings that are primarily near Stockton. The [Locations Page](https://cmcenters.org/locations/) on the second site @cmcenters lists all of the Stockton area locations. See the [Facilities Page](03_facilities.html) for a comprehensive list and map of all facilities. Also on their 2023 Form 990, they list their website as www.communitymedicalcenters.org, which redirects to the Stockton page @cmcenters

  - Clovis Community Medical Center
      - 2755 Herndon Avenue
      - Clovis, CA 93611
      - `(559) 324-4000`
  
  - Community Regional Medical Center
      - 2823 Fresno Street
      - Fresno, CA 93721
      - `(559) 459-6000`
  
  - Fresno Heart & Surgical Hospital
      - 15 E. Audubon Drive
      - Fresno, CA 93720
      - `(559) 433-8000`
  
  - Community Behavioral Health Center
      - 7171 N. Cedar Avenue
      - Fresno, CA 93720
      - `(559) 449-8000`
      
      
#### Form 990 {#sec-form-990}

A viewable version of Form 990 for CHCC @community_medical_centers can be seen at @viewable_990.

Below is basic information pulled from Giving Tuesday Data Commons @giving_tuesday_data_commons_990. For variable definitions see the data dictionary below @sec-form-990-dd.

```{r}
# GET request for giving Tuesday 990 data
resp_990 <- get_990(ein = "942437106") 
```


##### Select Fields
```{r}
#| output: true
resp_990$body$results %>% 
  select(id, TAXYEAR, TOTAEMPLCNTN, FILERNAME1, FILERUS1, FILERUSCITY, FILERUSSTATE, 
         FILERUSZIP, FORMATIONORM, GOVERNGRANTS, INFOTECHTOTA, MANAGENEEXPE, 
         ININTORECOOL, INTERETOTALO, LEGAFEESTOTA, NBREVOTIMEMB, OCCUPATOTALO, 
         OFFIEXPETOTA, ORGANIZATION3, OTHEMPBENTOT, OTHSALWAGTOT, PAYRTAXETOTA, 
         PENPLACONTOT, PROGSERVEXPE, TLNAEOY, TNAFBEOY, TOTREVCURYEA) %>% 
  rename_990() %>% 
  arrange(desc(tax_year)) %>% 
  DT::datatable(extensions = 'Buttons',
                options = list(
                  paging = TRUE,
                  searching = TRUE,
                  fixedColumns = TRUE,
                  autoWidth = TRUE,
                  ordering = TRUE,
                  dom = 'ftBlp',
                  buttons = c('copy', 'csv')
                  ),
                class = "display")
```



##### All Fields

```{r}
#| output: true
resp_990$body$results %>% 
  select(order(colnames(.))) %>% 
  relocate(id, TAXYEAR) %>% 
  arrange(desc(TAXYEAR)) %>% 
  DT::datatable(extensions = 'Buttons',
                options = list(
                  paging = TRUE,
                  searching = TRUE,
                  fixedColumns = TRUE,
                  autoWidth = TRUE,
                  ordering = TRUE,
                  dom = 'ftBlp',
                  buttons = c('copy', 'csv')
                  ),
                class = "display")
```

### Form 990 Data Dictionary {#sec-form-990-dd}

This table gives definitions for all of the variables in @sec-form-990.
```{r}
#| output: true
read_csv(here::here("data/Basic_Data_Dic_Giving_Tuesday_Data_Commons.csv")) %>% 
  arrange(`Variable Name`) %>% 
  DT::datatable(extensions = 'Buttons',
                options = list(
                  paging = TRUE,
                  searching = TRUE,
                  fixedColumns = TRUE,
                  autoWidth = TRUE,
                  ordering = TRUE,
                  dom = 'ftBlp',
                  buttons = c('copy', 'csv')
                  ),
                class = "display")
```


## Strategy

  - CHCC @community_medical_centers is a non-profit primarily based in the Stockton area, with only 4 medical centers near Fresno. It could be a point of agitation to the community of Fresno that an out-of-town organization is the one that owns their hospitals.