---
title: "2. Operations"
format: html
---

```{r}
library(tidyverse)
library(downloadthis)
library(DT)
source(here::here('functions/load_functions.R'))
load_functions()
```

```{r}
# NOTE: Best to run this in console since
# save latest NCCS data. Only need to run if new data available
#download_nccs()
```

```{r}
# load nccs data from local and get CHCC data
df_nccs <- load_nccs(year = "2025",
                     month = "01") %>% 
  filter(EIN == 942437106)
```

## About

The [About Page](https://cmcenters.org/about/) on the CHCC @community_medical_centers website says:

>At Community Medical Centers (CMC), we’re passionate about improving health and well-being in the communities we call home. That’s why we work to ensure even our most vulnerable neighbors have affordable access to quality healthcare, regardless of age, income, or background.
  We offer integrated medical, dental, behavioral health, and supportive services, with a model of care that puts the patient at the center of a team-based approach. As one of the region’s largest healthcare providers, our growing network of neighborhood health centers serves over 100,000 patients in San Joaquin and Solano counties.

## National Taxonomy of Exempt Entities

Community Hospitals of Central California's NTEE Code: 
**`r df_nccs %>% pull(NTEE_CD)`**

Noting that the Urban Institute's National Center for Charitable Statistics Website @ui_nccs has a list of NTEE codes. E300 is not among them. However, E30 appears in the list with
the following description:

**Ambulatory & Primary Health Care**

> Health centers, clinics, and other facilities that provide walk-in, walk-out diagnostic and treatment services for people whose care does not require confinement or a hospital stay. Use this code for types of outpatient facilities or services not specified below.

## Services
The [Services Page](https://cmcenters.org/services/) on the CHCC @community_medical_centers website
lists the following services:

  - Adult Medicine
  - Behavioral Health
  - Dental Care
  - Care Link Community Outreach
  - Pediatrics and Adolescent Health
  - Pharmacy
  - Recovery
  - Women's Health
  - Health Coverage Counseling
  - Health Education
  - Women, Infants and Children Program (WIC)

## Facilities



## Workforce
## Suppliers
## Procurement/ Distribution
## Customers/Clients
## Utilities
## Subsidiaries
