---
title: "2. Operations"
format: html
---

```{r}
library(tidyverse)
library(downloadthis)
library(DT)
source(here::here('functions/load_functions.R'))
load_functions()
```

```{r}
# NOTE: Best to run this in console since it is interactive.
# Save latest NCCS data. Only need to run if new data available
#download_nccs()
```

```{r}
# load nccs data from local (above chunk) and get CHCC data
df_nccs <- load_nccs(year = "2025",
                     month = "01") %>% 
  filter(EIN == 942437106)
```

## National Taxonomy of Exempt Entities

Community Hospitals of Central California's NTEE Code: 
**`r df_nccs %>% pull(NTEE_CD)`**

Noting that the Urban Institute's National Center for Charitable Statistics Website @ui_nccs has a list of NTEE codes. E300 is not among them. However, E30 appears in the list with
the following description:

**Ambulatory & Primary Health Care**

> Health centers, clinics, and other facilities that provide walk-in, walk-out diagnostic and treatment services for people whose care does not require confinement or a hospital stay. Use this code for types of outpatient facilities or services not specified below.

## About

The [About Page](https://www.communitymedical.org/about-us) on the CHCC @community_medical_centers (and NOT the Stockton based cmcenters) website says:

>   We operate four hospitals and a cancer institute, along with several long-term care, 
outpatient and other healthcare facilities.
    We're led by local leaders and physicians focused on addressing the diverse needs and issues of Central California. As the leading healthcare provider in the central San Joaquin Valley, Community cares for more people in the region than any other.
    That means regardless of income level or social demographics, we provide top notch care to support the health and well-being of those in need.
    We partner with UCSF — one of the world's top three medical schools and recruit physicians from around the country and world to bring you new specialties and treatments.
    By creating an environment of innovation and adding advanced medical technologies to our repertoire, we assure the care you receive from the Community Medical Centers healthcare network will continue to be second-to-none.

They also have a [Community Benefit Page](https://www.communitymedical.org/about-us/our-impact#comm_benefit) that explicitly says under the heading "Access to Healthcare":

> Goal: Increase access to healthcare services through primary care, preventative care and specialty care services, including HIV/AIDS/STIs, for medically underserved residents

## Services

The [Services Page](https://www.communitymedical.org/specialties-and-departments) on the CHCC @community_medical_centers website has a long list of medical services they provide, each with
its own dedicated page


## Quality and Safety Measures

::: {.callout-important title="Potential Argument"}
It's worth noting that their [Quality & Safety Measures](https://www.communitymedical.org/for-patients-families/quality-measures) page gives 5 outcome measures by 3 locations at the hospital, state, and national level. As they present it, the Clovis facilities have **worse** outcomes than the others. Notably, these are all emergent or acute measures.
:::









