---
title: "4. Workforce"
format: html
---

```{r}
library(tidyverse)
source(here::here('functions/load_functions.R'))
load_functions()
```

## Employees

From the viewable 2023 Form 990 @viewable_990, the total number of employees for the
2022 calendar year was **1,336**. See historical numbers below: 
```{r}
# pull 990 history
resp_990 <- get_990(ein = "942437106") 
```

```{r}
#| output: true
resp_990$body$results %>% 
  select(id, TAXYEAR, TOTAEMPLCNTN, FILERNAME1, FILERUS1, FILERUSCITY, FILERUSSTATE, 
         FILERUSZIP, FORMATIONORM, GOVERNGRANTS, INFOTECHTOTA, MANAGENEEXPE, 
         ININTORECOOL, INTERETOTALO, LEGAFEESTOTA, NBREVOTIMEMB, OCCUPATOTALO, 
         OFFIEXPETOTA, ORGANIZATION3, OTHEMPBENTOT, OTHSALWAGTOT, PAYRTAXETOTA, 
         PENPLACONTOT, PROGSERVEXPE, TLNAEOY, TNAFBEOY, TOTREVCURYEA) %>% 
  rename_990() %>% 
  select(tax_year,
         num_employees) %>% 
  arrange(desc(tax_year)) %>% 
  DT::datatable(extensions = 'Buttons',
                options = list(
                  paging = TRUE,
                  searching = TRUE,
                  fixedColumns = TRUE,
                  autoWidth = TRUE,
                  ordering = TRUE,
                  dom = 'ftBlp',
                  buttons = c('copy', 'csv')
                  ),
                class = "display")
```

## NLRB Activity

Note that I've removed the Participants field from the below table because it is too long. If complete participant information is desired, the details of any case can be found using the Case Number in the NLRB Case Search @nlrb_case_search.

However, unions mentioned include:

  * SEIU UNITED HEALTHCARE WORKERS - WEST, Stockton, CA
  * SEIU UNITED HEALTHCARE WORKERS - WEST, Fresno, CA
  * SERVICE EMPLOYEES INTERNATIONAL UNION, Washington, DC
  * CALIFORNIA NURSES ASSOCIATION NATIONAL NURSES ORGANIZING COMMITTEE (CNA/NNOC) Sacramento, CA, AFL-CIO, Fresno, CA
  * STATIONARY ENGINEERS, LOCAL UNION 39
  * INTERNATIONAL UNION OF OPERATING ENGINEERS, AFL-CIO, Sacramento, CA

```{r}
df_nlrb <- bind_rows(
  read_csv(here::here("data/nlrb_cases_clovis_cmc.csv")),
  read_csv(here::here("data/nlrb_cases_fresno_cmc.csv"))
)
```

```{r}
#| output: true
df_nlrb %>% 
  select(-Participants) %>% 
  table_standard()
```